sims

### 2024-10-30 sims/sims.Rmd
typo fixed
updates to the sim files and figs

use a truncated normal distribution to privude upper and lower bounds

```{r}
rt_dat_test <- data_n10 %>%
  select(-contrast, -event, -cumsum, -outcomel) %>% 
  mutate(u = bin*100,
         l = u-100,
         m = (l + u)/2) %>% 
  filter(outcomen > 0) %>% 
  group_by(subj, rep, condition, bin) %>% 
  mutate(rt = rtruncnorm(n=1, mean=m, sd=25, a=l, b=u))
head(rt_dat_test)
summary(rt_dat_test)
```

@@

```{r}
rt_dat <- function(df) {
  df %>%
    select(-contrast, -event, -cumsum, -outcomel) %>% 
    mutate(u = bin*100,
         l = u-100,
         m = (l + u)/2) %>% 
    filter(outcomen > 0) %>% 
    group_by(subj, rep, condition, bin) %>% 
    mutate(rt = rtruncnorm(n=1, mean=m, sd=25, a=l, b=u)) %>% 
    ungroup()
}
```

@@

@@

@@

```{r}
p_haz_inset_facet <- p8.1 +
  geom_plot(data = inset_facet,
            vp.width = 1/3,
            aes(x, y, label = plot))
p_haz_inset_facet

ggsave("sims/figures/haz_inset_facet.jpeg",
       width = 14, height = 10, dpi=1000)
```

@@

>>>>

use a uniform distribution to provide upper and lower bounds

```{r}
rt_dat_test <- data_n10 %>%
  select(-contrast, -event, -cumsum, -outcomel) %>% 
  mutate(u = bin*100,
         l = u-100,
         m = (l + u)/2) %>% 
  filter(outcomen > 0) %>% 
  group_by(subj, rep, condition, bin) %>% 
  # mutate(rt = rtruncnorm(n=1, mean=m, sd=25, a=l, b=u))
  mutate(rt = runif(n=1, min=l, max=u))
head(rt_dat_test)
summary(rt_dat_test)
```

@@

```{r}
rt_dat <- function(df) {
  df %>%
    select(-contrast, -event, -cumsum, -outcomel) %>% 
    mutate(u = bin*100,
         l = u-100,
         m = (l + u)/2) %>% 
    filter(outcomen > 0) %>% 
    group_by(subj, rep, condition, bin) %>% 
    mutate(rt = runif(n=1, min=l, max=u)) %>% 
    ungroup()
}
```

@@

re-plot with 2 columns, rather than 2 rows, and re-order the facets so that 1-3 are in col1

```{r}
p8.1b <- haz_plot(haz_pid_all, haz_group_all) +
  facet_wrap(~fct_relevel(example,'example 1','example 4','example 2','example 5',
                          'example 3', 'example 6'), ncol = 2)
p8.1b
```

@@

re-plot rt with 2 columns, rather than 2 rows

```{r}
p8.2b <- rt_plot(rt_pid_all, rt_group_all) +
  facet_wrap(~example, ncol = 2)
p8.2b
```

@@

with two rows

```{r}
# p_haz_inset_facet <- p8.1 +
#   geom_plot(data = inset_facet,
#             vp.width = 1/3,
#             aes(x, y, label = plot))
# p_haz_inset_facet
# 
# ggsave("sims/figures/haz_inset_facet.jpeg",
#        width = 14, height = 10, dpi=1000)
```

with two columns

```{r}
p_haz_inset_facet <- p8.1b +
  geom_plot(data = inset_facet,
            vp.width = 1/3,
            aes(x, y, label = plot))
p_haz_inset_facet

ggsave("sims/figures/haz_inset_facet.jpeg",
       width = 10, height = 12, dpi=1000)
```

@@

# section 10 #
